Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-12 paper.tex
Finishing answer to density threshold

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}
\usepackage{hyperref}
%\usepackage{subcaption}
%\usepackage{caption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables 
having their usual definitions. The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units.}

@@

	\item molecular hydrogen fraction, f$_{\rm H2}$ > 10$^{-3}$
\end{enumerate}

@@

%====================================================================
\subsection{\hh{} Self-Shielding}
%====================================================================
We use the Sobolev-like approximation from \citet{Wolcott11} to model \hh{} self-shielding. To determine the \hh{} shielding factor, the column density of \hh{} needs to be calculated:
\begin{equation} \label{Nh2}
	N_{\rm H2} = n_{\rm H2}L_{\rm char} \ ,
\end{equation}
where n$_{\rm H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{\rm H2}$ is assumed to be constant. The method employed in this simulation is to define the characteristic length as:
\begin{equation} \label{Lchar}
	L_{\rm char} = \frac{\rho}{|\nabla \rho|} \ . 
\end{equation}
This Sobolev-like method determines the length over which gas with density $\rho$ is diminished. They found that the most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all Cartesian directions.

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}
%\usepackage[draft]{hyperref}
%\usepackage{subcaption}
%\usepackage{caption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  \textbf{We refine the cells one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units.}

@@

	\item molecular hydrogen fraction, f$_{\rm H2}$ > 10$^{-3}$
\end{enumerate}
%
\textbf{Our chosen threshold density corresponds to a value similar to a density that would trigger another mesh refinement past level 12.  At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.}

@@

%====================================================================
\subsection{\texorpdfstring{H$_2$} Self-Shielding}
%====================================================================
We use the Sobolev-like approximation from \citet{Wolcott11} to model \hh{} self-shielding. To determine the \hh{} shielding factor, the column density of \hh{} needs to be calculated:
\begin{equation} \label{Nh2}
	N_{\rm H2} = n_{\rm H2}L_{\rm char} \ ,
\end{equation}
where n$_{\rm H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{\rm H2}$ is assumed to be constant. The method employed in this simulation is to define the characteristic length as:
\begin{equation} \label{Lchar}
	L_{\rm char} = \frac{\rho}{|\nabla \rho|} \ . 
\end{equation}
This Sobolev-like method determines the length over which gas with density $\rho$ is diminished. They found that the most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all Cartesian directions.

### 2019-08-12 referee.tex
Finishing answer to density threshold

In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

@@

We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  At $T=300$ K, the Jeans length is $L_{\rm J} = 0.17$~pc at $\rho = 10^6 m_{\rm H}$~g/cm$^3$.  \textbf{JHW: finish this point.}

>>>>

In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.
q
\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

@@

Our choice was motivated by our refinement strategy rather than convergence. We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4 \cubecm$.  This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.  In the case where the density SF criterion is larger than $n$, the gas will continue to condense on a faster timescale than its surroundings.  Thus we are confident that this slight mismatch does not affect our results.

We have added the AMR refinement criteria to Section 2.1 and our motivation to this threshold to Section 2.2.1.
